Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
Only save depressive rows for the subgroups

# Ensure that 'Time.Period.End.Date' is a Date object
filtered_data$Time.Period.End.Date <- as.Date(filtered_data$Time.Period.End.Date, format = "%Y-%m-%d")

@@

@@

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

>>>>

# Ensure that 'Time.Period.End.Date' is a Date object
filtered_data$Date <- as.Date(filtered_data$Date, format = "%Y-%m-%d")

@@

# Ensure that 'Time.Period.End.Date' is a Date object
filtered_data$Date <- as.Date(filtered_data$Date, format = "%Y-%m-%d")

@@

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
```
